% --------------------------------------------------------------------------
% Reference Documents
% --------------------------------------------------------------------------

\section{Reference Documents}
\label{sec:refdocs}%

The preparation of this document was supported by the following reference materials:
\begin{itemize}
	\item Assignment specification for the ITD of the Software Engineering II course,
	      held by professors Matteo Rossi, Elisabetta Di Nitto, and Matteo Camilli at the
	      Politecnico di Milano, Academic Year 2025/2026 \cite{itd_spec};
	\item Slides of the Software Engineering II course available on WeBeep \cite{slides}.
	\item The delivered material of the Best Bike Paths project, including the RASD, DD, 
	and ITD documents provided by the authors Huang Shijie, Li Yuqing, and Ma Zeyao \cite{rasd, dd, itd}.
\end{itemize}

% --------------------------------------------------------------------------
% Software Used
% --------------------------------------------------------------------------

\section{Software Used}
\label{sec:software}

The following software tools have been used to support the development of this project:

\begin{itemize}
	\item \textbf{Visual Studio Code}: editing of source code and documentation (LaTeX), with project-wide search and formatting support \cite{vscode}.
	\item \textbf{LaTeX}: typesetting system used to produce the final RASD document in a consistent format \cite{latex}.
	\item \textbf{Git}: version control used to track changes and support collaborative development \cite{git}.
	\item \textbf{GitHub}: remote repository hosting and collaboration platform used for versioning, reviews, and issue tracking \cite{github}.
\end{itemize}

% --------------------------------------------------------------------------
% AI Tools Usage
% --------------------------------------------------------------------------

\section{Use of AI Tools}
\label{sec:ai}

AI tools were used during the project as supporting tools, in the same way as other software
adopted in the development process. Their role was not to automatically generate content, but
to help improve the clarity, structure, and overall quality of the documentation.

\subsection{Tools Used}
The AI tools employed during the project were:
\begin{itemize}
	\item Gemini
	\item ChatGPT
\end{itemize}

\subsection{Typical Prompts}
AI tools were queried using prompts such as:
\begin{itemize}
	\item "Rephrase this description to make it clearer."
	\item "Does this explanation of the error encountered contain any ambiguities?"
	\item "Suggest alternative wording for this paragraph to improve readability."
\end{itemize}

\subsection{Input Provided}
The input given to AI tools consisted mainly of:
\begin{itemize}
	\item Early drafts of paragraphs.
	\item Short text fragments requiring clarity checks.
	\item Sections with repeated structure where consistent wording was needed.
\end{itemize}

\subsection{Constraints Applied}
When using AI tools, the following constraints were strictly enforced:
\begin{itemize}
	\item Preserve the intended meaning of the original text.
	\item Avoid introducing new design decisions or assumptions.
	\item Maintain terminology aligned with the definitions provided in this document.
\end{itemize}

\subsection{Outputs Obtained}
The interaction with AI tools resulted in:
\begin{itemize}
	\item Clearer or more concise formulations of existing statements.
	\item Identification of potentially ambiguous sentences.
	\item Terminology suggestions to improve internal coherence.
\end{itemize}

\subsection{Refinement Process}
All AI-generated outputs were subject to a manual refinement process that included:
\begin{itemize}
	\item Critical review of all suggestions.
	\item Verification against the original intent to avoid unintended changes.
	\item Manual integration to ensure consistency with the overall writing style.
	\item Alignment checks with established terminology and definitions.
\end{itemize}
