% --------------------------------------------------------------------------
% OVERALL DESCRIPTION % 
% --------------------------------------------------------------------------
\subsection{Purpose}
This document aims to describe how the implementation and integration testing took place.
Implementation is the last step of the Best Bike Path application development cycle.

Testing, instead, means check that the critical parts of the application works in a correct way, as described in the DD document.

The code and the releases can be find on the official CLup repository hosted on GitHub, reachable at this link:\\ \href{https://github.com/BIA3IA/Errigo-Gholami-Ianosel}{https://github.com/BIA3IA/Errigo-Gholami-Ianosel}.

\subsection{Definitions, Acronyms, Abbreviations}
\subsubsection{Acronyms}
\begin{itemize}
    \item \textbf{API:} Application Programming Interface.
    \item \textbf{APK:} Android Package
    \item \textbf{DBMS:} DataBase Management System.
    \item \textbf{DD:} Design Document.
    \item \textbf{DOM:} Document Object Model.
    \item \textbf{DTO:} Data Transfer Object, represents a link between the user input and a Java Object.
    \item \textbf{HTTP:} HyperText Transfer Protocol.
    \item \textbf{IPA:} iOS App Store Package.
    \item \textbf{JPA:} Java Persistence API.
    \item \textbf{JS:} JavaScript.
    \item \textbf{QR Code:} Quick Response Code.
    \item \textbf{REST:} REpresentational State Transfer (see DD).
    \item \textbf{RASD:} Requirements Analysis and Specification Document.
    \item \textbf{S2B:} Software To Be.
    \item \textbf{UI:} User Interface.
    \item \textbf{URL:} Uniform Resource Locator.
    \item \textbf{UX:} User eXperience.
    \item \textbf{ORM:} Object-Relational Mapping.
\end{itemize}

\subsubsection{Abbreviations}
\begin{itemize}
    \item \textbf{something:} 
\end{itemize}

\subsection{Revision history}
\begin{itemize}
    \item January 28, 2026: version 1.0 (first release)
    \item February 7, 2026: version 1.1 (fixed some typos)
\end{itemize}

\subsection{References}
\label{references}
\begin{itemize}
    \item \textbf{Dart} \href{https://dart.dev/}{https://dart.dev/}
    \item \textbf{Easy Loading} \href{https://pub.dev/packages/easy_loading}{https://pub.dev/packages/easy\_loading}
    \item \textbf{Flutter Barcode Scanner} \href{https://pub.dev/packages/flutter_barcode_scanner}{https://pub.dev/packages/flutter\_barcode\_scanner}
    \item \textbf{Flutter Local Notification} \href{https://pub.dev/packages/flutter_local_notifications}{https://pub.dev/packages/flutter\_local\_notifications}
    \item \textbf{Flutter Printing} \href{https://pub.dev/packages/printing}{https://pub.dev/packages/printing}
    \item \textbf{Flutter} \href{https://flutter.dev/}{https://flutter.dev/}
    \item \textbf{Font Awesome} \href{https://fontawesome.com/}{https://fontawesome.com/}
    \item \textbf{Google Fonts} \href{https://fonts.google.com/}{https://fonts.google.com/}
    \item \textbf{Google Maps Flutter} \href{https://pub.dev/packages/google_maps}{https://pub.dev/packages/google\_maps}
    \item \textbf{Hive} \href{https://pub.dev/packages/hive}{https://pub.dev/packages/hive}
    \item \textbf{Java: } \href{https://www.java.com/it}{https://www.java.com/it}
    \item \textbf{JavaScript: } \href{https://www.javascript.com}{https://www.javascript.com}
    \item \textbf{jQuery: } \href{https://jquery.com}{https://jquery.com}
    \item \textbf{Kotlin} \href{https://kotlinlang.org/}{https://kotlinlang.org/}
    \item \textbf{Leaflet.js} \href{https://leafletjs.com}{https://leafletjs.com}
    \item \textbf{Pull to refresh} \href{https://pub.dev/packages/pull_to_refresh}{https://pub.dev/packages/pull\_to\_refresh}
    \item \textbf{QR Flutter} \href{https://pub.dev/packages/qr_flutter}{https://pub.dev/packages/qr\_flutter}
    \item \textbf{QRcode.js: } \href{https://jquery.com}{https://jquery.com}
    \item \textbf{Semantic UI: } \href{https://semantic-ui.com}{https://semantic-ui.com}
    \item \textbf{Spring Framework: } \href{https://spring.io}{https://spring.io}
    \item \textbf{Spring Security: } \href{https://spring.io/projects/spring-security}{https://spring.io/projects/spring-security}
    \item \textbf{Spring Social: } \href{https://projects.spring.io/spring-social}{https://projects.spring.io/spring-social}
    \item \textbf{Swift} \href{https://www.apple.com/it/swift/}{https://www.apple.com/it/swift/}
    \item \textbf{Url Launcher} \href{https://pub.dev/packages/url_launcher}{https://pub.dev/packages/url\_launcher}
    \item \textbf{Vue.js: } \href{https://vuejs.org}{https://vuejs.org}
\end{itemize}
