The BBP platform can be used in different configurations, depending on the intended use case and on whether
the user aims to simply run the application or to actively develop and test it.

In particular, three main usage scenarios are supported:
\begin{itemize}
	\item \textbf{Remote backend with prebuilt mobile application}: the user installs a prebuilt APK and interacts with an already deployed backend instance.
	\item \textbf{Fully local execution}: both the backend services and the mobile application are executed locally for development and testing purposes.
	\item \textbf{Hybrid configuration}: the mobile application is run locally while relying on a remotely deployed backend.
\end{itemize}

\section{Prerequisites}
\label{sec:prerequisites}

To run the BBP platform locally, a set of prerequisites must be satisfied to ensure a consistent and
reproducible development environment.

\begin{itemize}
	\item \textbf{Node.js and npm}: required to manage dependencies and execute project scripts for both the
	      backend services and the mobile application. All build, test, and development workflows rely on the Node.js runtime.

	\item \textbf{Docker and Docker Compose}: required to run backend services and auxiliary components in isolated
	      containers. In the local setup, Docker Compose is used to start the BBP backend, the PostgreSQL database,
	      and the OSRM routing service, ensuring a configuration that closely mirrors the production environment without
	      requiring manual installation of these components on the host system.

	\item \textbf{Expo CLI}: required to run the mobile application locally during development. It is used to
	      start the Metro bundler and to enable live previews of the application on emulators or physical devices.

	\item \textbf{Expo Go}: required on a physical mobile device to preview the application during development
	      by connecting to the local Metro bundler started via Expo CLI. May be replaced with an emulator.
\end{itemize}

\section{Backend Setup}
\label{sec:backend_setup}

The BBP backend can be executed either as a remotely deployed service or as a locally running instance
for development and testing purposes.

\subsection{Production Deployment}
\label{subsec:backend_production}

The BBP backend is deployed on a \textbf{VPS} using a \textbf{container-based architecture} built on Docker
and Docker Compose. The service is designed to coexist with other applications hosted on the same server
while remaining isolated and not directly exposed to the public network.

The backend application runs as a stateless service inside \textbf{Docker containers} and listens on port 3000,
which is reachable only within the container network. No backend container exposes public ports on the
host system. All incoming traffic is handled by a \textbf{shared NGINX reverse proxy}, which is the only component
exposing ports 80 and 443.

NGINX acts as the \textbf{single entry point} for the system and is responsible for HTTPS termination, request
routing, load balancing, and basic traffic filtering. TLS is managed using \textbf{Cloudflare Origin Certificates},
with Cloudflare acting as \textbf{DNS provider and upstream security layer}. Requests validated by Cloudflare are
forwarded to the reverse proxy, which then routes them to the backend service.

The backend is horizontally scalable and is deployed using \textbf{multiple container replicas}. In the current
configuration, three backend instances are executed in parallel. NGINX resolves backend containers
dynamically using \textbf{Docker’s embedded DNS} and \textbf{balances incoming requests} across replicas through an
upstream definition. This approach allows the system to scale without introducing a dedicated load
balancer and ensures high availability of the API layer.

The deployment process starts by copying the backend project files to the server. This can be performed
from a local machine using a secure file transfer mechanism, for example:

\begin{verbatim}
rsync -avz ./BACKEND/ user@<SERVER_IP>:/opt/bbp-backend/
\end{verbatim}

Once the project is available on the server, environment-specific configuration values are provided
through a dedicated \textbf{.env} file. This file defines runtime parameters such as authentication
secrets, database connection details, and service timeouts. Sensitive values are \textbf{never committed} to
version control and are configured directly on the server.

The backend is built and started using \textbf{Docker Compose}. A shared \textbf{Docker network}
is created once and is used to connect the reverse proxy, backend replicas, and auxiliary services.
The backend containers join this network and expose port 3000 only internally. The services can be
built and started with the following commands:

\begin{verbatim}
docker compose build --no-cache
docker compose --profile tools run --rm migrate
docker compose up -d --scale api=3
\end{verbatim}

Database \textbf{migrations} are executed explicitly through a dedicated migration container and are only run
when schema changes are introduced. This avoids unintended schema modifications during routine
restarts.

Persistent data storage is handled through \textbf{PostgreSQL} accessed via \textbf{Prisma Accelerate}. This configuration
allows the backend to rely on a \textbf{managed database connection layer} without hosting a database instance
directly on the server, while still preserving transactional guarantees and schema consistency.

Caching of data relies on \textbf{Redis}, which runs alongside the backend in the same
server environment and is reachable only inside the internal Docker network. The backend connects using the
environment variables \textbf{REDIS\_HOST} and \textbf{REDIS\_PORT}, and uses Redis as a cache layer while
keeping the database as the source of truth.

In addition to the core backend service, snapping-related functionalities are delegated to a separate
\textbf{OSRM service}, which runs in its own container. OSRM is responsible for snapping user-defined paths to
the OpenStreetMap road network using a cycling profile. The backend communicates with OSRM through an
internal HTTP interface and exposes a dedicated API endpoint to the mobile application.

After deployment, the backend can be verified by inspecting container status and logs:

\begin{verbatim}
docker compose ps
docker logs -f bbp-backend-api-1 --tail=50
\end{verbatim}

A dedicated \textbf{health endpoint} is exposed and can be used by the reverse proxy to verify service
availability. If correctly deployed, the backend responds to authenticated API requests through the
public API endpoint exposed by the reverse proxy.

\subsection{Local Backend Execution}
\label{subsec:backend_local}

For local development and testing, the BBP backend can be executed using a Docker-based setup that mirrors
the production environment, while enabling development-specific features such as live reload.
To keep the production configuration unchanged, the local development setup is defined
through an additional Docker Compose file and a dedicated development Dockerfile.

Before starting the backend locally, developers must ensure they are operating from the backend project
directory, which contains the production \textbf{docker-compose.yml}, the development override
\textbf{docker-compose.dev.yml}, and the related \textbf{Dockerfile.dev}. All commands must be executed
from this directory.

The development configuration builds the backend image using \textbf{Dockerfile.dev} and runs the service
with \textbf{NODE\_ENV=development}. Project source files are mounted into the container through bind mounts,
so changes to the codebase are immediately reflected without rebuilding the image. Node.js dependencies
are installed inside the container during the image build and are not required on the host system.

Environment-specific configuration values are provided through a dedicated \textbf{.env} file located in
the backend project directory. This file defines authentication secrets, database connection parameters,
and service endpoints. Additional local-only variables can be added when needed without affecting the
production configuration.

To build and start the backend locally, the development override is applied on top of the base
configuration using Docker Compose:

\begin{verbatim}
docker compose -f docker-compose.yml -f docker-compose.dev.yml up -d
 --build
\end{verbatim}

Once the backend container is running, application logs can be inspected in real time to monitor startup
and runtime behavior:

\begin{verbatim}
docker logs -f bbp-backend-api --tail=50
\end{verbatim}

A basic health check endpoint is exposed by the backend and can be used to verify that the service is
running correctly:

\begin{verbatim}
curl -i http://localhost:3000/health
\end{verbatim}

In the development configuration, port 3000 is published on the host system. As a result, the backend API
is available at \textbf{http://localhost:3000} and can be accessed by the mobile application or by API
testing tools.

Automated tests can be executed directly inside the running backend container. This allows tests to run
in the same environment as the application, without requiring local dependency installation. Tests can be
started with:

\begin{verbatim}
docker compose -f docker-compose.yml -f docker-compose.dev.yml 
exec api npm run test
\end{verbatim}

When the local backend is no longer needed, all running services can be stopped and removed using Docker
Compose:

\begin{verbatim}
docker compose -f docker-compose.yml -f docker-compose.dev.yml down
\end{verbatim}

This command stops and removes the containers associated with the local development environment without
affecting images or configuration files.
All backend services can be stopped and restarted at any time without affecting the host system, as the
entire runtime environment is isolated within containers.

\subsection{Backend Services in Local Development}
\label{subsec:backend_services_local}

Some backend functionalities depend on external services. In a local
development environment, these services behave differently depending on their availability and deployment
model.

Caching of trip and statistics data relies on \textbf{Redis}, which is required for the backend to operate
correctly. In local development, Redis starts together with the backend using Docker Compose.
Connection settings are controlled via \textbf{REDIS\_HOST} and \textbf{REDIS\_PORT}.

Weather-related features rely on the \textbf{Open-Meteo} service. This integration works out of the box
in local development, as Open-Meteo provides a public API that does not require authentication or API
keys.

Geocoding functionalities are handled through \textbf{Nominatim}. In the local setup, no additional
configuration is required, as the backend uses the public Nominatim API to resolve textual addresses into
geographic coordinates.

Path snapping functionalities depend on \textbf{OSRM} (Open Source Routing Machine). Unlike the previous
services, OSRM is not a public API and must be explicitly deployed as a separate service. In the production
environment, OSRM runs as a dedicated container and is accessed by the backend through an internal HTTP
interface. In a local development setup, OSRM is not available by default.

As a result, snapping-related features are disabled locally unless an OSRM instance is explicitly
configured. Developers who need to test path snapping locally have to deploy OSRM locally by following
the OSRM deployment procedure, which involves downloading OpenStreetMap extracts, preprocessing the dataset,
and running the OSRM service inside a Docker container.

\section{Frontend Setup}
\label{sec:frontend_setup}

The BBP mobile application can be used either as a prebuilt artifact connected to the production backend
or as a locally executed application for development and testing purposes.

\subsection{Deployed Mobile Application}
\label{subsec:frontend_deployed}

The deployed version of the BBP mobile application is distributed as a prebuilt Android \textbf{APK}.
This configuration is intended for demonstration, evaluation, and production usage scenarios where no
local development environment is required.

Users can install the APK directly on their Android device and immediately start using the application.
In this setup, the mobile client connects to the remotely deployed backend instance exposed through the
public API endpoint. All backend services, including authentication, path discovery, trip management, and
report handling, are accessed through the production infrastructure.

\subsection{Local Mobile Application Execution}
\label{subsec:frontend_local}

For development and testing purposes, the BBP mobile application can be executed locally using
\textbf{Expo CLI}. This configuration enables rapid iteration, hot reload, and debugging during frontend
development.

The application can be run either on a physical mobile device using \textbf{Expo Go} or on an Android or
iOS emulator. In both cases, Expo CLI starts the Metro bundler locally and serves the application bundle
to the target device.

Before starting the application, developers must ensure they are operating from the mobile application
project directory. Dependencies are installed using npm, and the development server is started as follows:

\begin{verbatim}
npx expo start
\end{verbatim}

During local execution, the mobile application can be configured to target either the production backend
or a locally running backend instance. This is controlled through environment variables defined in a
\texttt{.env} file. In particular, the API base URL must be updated to point to the desired backend
endpoint before starting the Expo development server.

When connected to a locally running backend, this setup allows developers to test end-to-end flows,
including authentication, path search, trip recording, and report submission.
Unlike the prebuilt APK, the locally executed application fully supports configuration changes.
