\begin{longtable}{|p{0.07\textwidth}|>{\raggedright\arraybackslash}p{0.55\textwidth}|>{\raggedright\arraybackslash}p{0.33\textwidth}|}
	\hline
	\textbf{Rx}  & \textbf{Description}                                                                                                                            & \textbf{Components}                                                         \\ \hline
	\endfirsthead

	\hline
	\textbf{Rx}  & \textbf{Description}                                                                                                                            & \textbf{Components}                                                         \\ \hline
	\endhead

	\hline
	\multicolumn{3}{|r|}{Continued on next page}                                                                                                                                                                                                 \\ \hline
	\endfoot

	\endlastfoot

	\textbf{R1}  & The system shall allow guest users to create an account by providing personal information and credentials.                                      & AuthManager, QueryManager                                                   \\ \hline

	\textbf{R2}  & The system shall allow registered users to log into the application using valid credentials.                                                    & AuthManager, QueryManager                                                   \\ \hline

	\textbf{R3}  & The system shall allow logged-in users to view their profile and account settings.                                                              & UserManager, QueryManager                                                   \\ \hline

	\textbf{R4}  & The system shall allow logged-in users to update their profile and account settings.                                                            & UserManager, QueryManager                                                   \\ \hline

	\textbf{R5}  & The system shall allow logged-in users to log out of the application, ending their current session.                                             & AuthManager, QueryManager                                                   \\ \hline

	\textbf{R6}  & The system shall allow guest users to start a cycling trip.                                                                                     & (*)                                                                         \\ \hline

	\textbf{R7}  & The system shall allow guest users to stop a currently active trip, but shall not store any trip data after the trip ends.                      & (*)                                                                         \\ \hline

	\textbf{R8}  & The system shall allow the user to start a trip only when their GPS position matches the path origin.                                           & (**)                                                                        \\ \hline

	\textbf{R9}  & The system shall display a pop-up suggesting to start a trip when cycling is detected while no trip is active and the app is open.              & (**)                                                                        \\ \hline

	\textbf{R10} & The system shall set the current GPS position as trip origin when starting from auto-detection.                                                 & (**)                                                                        \\ \hline

	\textbf{R11} & The system shall automatically stop the active trip when the user's GPS position deviates from the selected path within a certain threshold.    & (**)                                                                        \\ \hline

	\textbf{R12} & The system shall allow logged-in users to start a cycling trip in manual or automatic mode.                                                     & (**)                                                                        \\ \hline

	\textbf{R13} & The system shall allow logged-in users to stop a currently active trip and save the recorded data.                                              & TripManager, StatsManager, QueryManager, WeatherService                     \\ \hline

	\textbf{R14} & The system shall collect GPS data during trip recording.                                                                                        & (**)                                                                        \\ \hline

	\textbf{R15} & The system shall collect motion sensor data (accelerometer, gyroscope) during trip recording only when Automatic Mode is enabled.               & (**)                                                                        \\ \hline

	\textbf{R16} & The system shall allow logged-in users to view the list of their recorded trips.                                                                & TripManager, QueryManager                                                   \\ \hline

	\textbf{R17} & The system shall allow logged-in users to view a summary of their overall cycling statistics (total distance, total time, average speed, etc.). & StatsManager, QueryManager                                                  \\ \hline

	\textbf{R18} & The system shall allow logged-in users to view statistics for each trip (distance, speed, duration, etc.).                                      & StatsManager, QueryManager                                                  \\ \hline

	\textbf{R19} & The system shall display the route and reported obstacles associated with a recorded trip.                                                      & TripManager, ReportManager, QueryManager                                    \\ \hline

	\textbf{R20} & The system shall allow logged-in users to delete a recorded trip.                                                                               & TripManager, QueryManager                                                   \\ \hline

	\textbf{R21} & The system shall communicate with external weather services to retrieve meteorological data related to the time and location of a trip.         & TripManager, WeatherService                                                 \\ \hline

	\textbf{R22} & The system shall detect when a user is cycling based on speed and acceleration patterns.                                                        & (**)                                                                        \\ \hline

	\textbf{R23} & The system shall detect irregular movements from sensor data that may suggest potholes or surface defects when Automatic Mode is enabled.       & (**)                                                                        \\ \hline

	\textbf{R24} & The system shall present automatically detected path and obstacle data to the logged-in user for manual confirmation before publishing.         & (**)                                                                        \\ \hline

	\textbf{R25} & The system shall allow logged-in users to manually create a new bike path by drawing segments.                                                  & PathManager, QueryManager, SnappingService                                  \\ \hline

	\textbf{R26} & The system shall allow logged-in users to manually report obstacles or problems on a bike path while performing an active trip.                 & ReportManager, QueryManager                                                 \\ \hline

	\textbf{R27} & The system shall allow logged-in users to manually confirm or reject the presence of obstacles reported by other users.                         & ReportManager, QueryManager                                                 \\ \hline

	\textbf{R28} & The system shall allow logged-in users to create a new bike path in automatic mode using GPS tracking.                                          & PathManager, QueryManager                                                   \\ \hline

	\textbf{R29} & The system shall allow logged-in users to delete their previously created paths.                                                                & PathManager, QueryManager                                                   \\ \hline

	\textbf{R30} & The system shall allow logged-in users to set the visibility of their created paths as public or private.                                       & PathManager, QueryManager                                                   \\ \hline

	\textbf{R31} & The system shall aggregate multiple user reports referring to the same path segment.                                                            & ReportManager, PathManager, QueryManager                                    \\ \hline

	\textbf{R32} & The system shall evaluate the reliability of each path segment based on the number of confirmations and report freshness.                       & ReportManager, PathManager                                                  \\ \hline

	\textbf{R33} & The system shall determine the current status of a path (optimal, medium, sufficient, requires maintenance, closed).                            & ReportManager, PathManager                                                  \\ \hline

	\textbf{R34} & The system shall allow any user (guest or logged-in) to view the detailed status and latest reports of a selected bike path.                    & PathManager, ReportManager, QueryManager                                    \\ \hline

	\textbf{R35} & The system shall allow any user (guest or logged-in) to browse available public bike paths on a map.                                            & PathManager, QueryManager                                                   \\ \hline

	\textbf{R36} & The system shall allow any user to search for bike paths connecting two locations.                                                              & PathManager, QueryManager, GeocodingService                                 \\ \hline

	\textbf{R37} & The system shall compute suggested routes based on path quality and distance.                                                                   & PathManager                                                                 \\ \hline

	\textbf{R38} & The system shall rank suggested routes according to their safety and quality.                                                                   & PathManager                                                                 \\ \hline

	\textbf{R39} & The system shall display the user's current GPS position during navigation along a selected path.                                               & (**)                                                                        \\ \hline

	\textbf{R40} & The system shall send pop-ups to warn users about nearby obstacles or closed path segments during an active trip.                               & (**)                                                                        \\ \hline

	\textbf{R41} & The system shall interface with map and geocoding services to translate addresses into coordinates and render paths.                            & PathManager, GeocodingService                                               \\ \hline

	\textbf{R42} & The system shall ensure that communication with all external services (map, weather) handles temporary unavailability gracefully.               & PathManager, TripManager, WeatherService, GeocodingService, SnappingService \\ \hline

	\caption{Mapping between BBP Requirements and Backend Components}
	\label{tab:R_MAP}
\end{longtable}

(*) The trip management functionality for guest users is limited to starting and stopping trips without data persistence. No communication with backend components occurs in this mode.

(**) These functionalities are implemented on the client side and do not involve backend components.